\begin{thebibliography}{}
    \bibitem{} Andrea Macchi, Giovanni Moruzzi, Francesco Pegoraro, \textit{Problems in Classical Electromagnetism: 157 Exercises with Solutions}, Springer.
    \bibitem{} Edward M.Purcell and David.J.Morin, \textit{Electricity and Magnetism}, Cambridge University Press.
    \bibitem{} Teruo Matsushita, \textit{Electricity and Magnetism: New Formulation by Introduction of Superconductivity (Undergraduate Lecture Notes in Physics)}, Springer.
    \bibitem{} David.J.Griffiths, \textit{Introduction to Electrodynamics}, Cambridge University Press.
    \bibitem{} Péter Gnädig, Gyula Honyek and Ken Riley, \textit{200 Puzzling Physics Problems: With Hints and Solutions}, Cambridge University Press.
    \bibitem{} Péter Gnädig, Gyula Honyek and Máté Vigh, \textit{200 More Puzzling Physics Problems: With Hints and Solutions}, Cambridge University Press.
    \bibitem{} Sidney B. Cahn, Boris E. Nadgorny, \textit{A Guide to Physics Problems, Part 1: Mechanics, Relativity, and Electrodynamics (The Language of Science)}, Springer.
    \bibitem{} Lim Yung-kuo, The Physics Coaching Class University of Science and Technology of China, \textit{Problems and Solutions on Electromagnetism (Major American Universities Ph.D. Qualifying Questions and Solutions)}, World Scientific Publishing Company. 
    \bibitem{} Vũ Thanh Khiết, Phạm Khánh Hội, \textit{Đề thi học sinh giỏi Vật lí trung học phổ thông}, NXB Giáo dục Việt Nam.
\end{thebibliography}
\hfill \\
    Sách chọn lọc và tuyển tập từ các nguồn đề thi Olympic các quốc gia, khu vực và quốc tế:
    \setcounter{enumiv}{0}
    \begin{enumerate}[{[}1{]}]
    \item Romanian Physics Olympiad
    \item Estonian Physics Olympiad
    \item Chinese Physics Olympiad $-$ CPhO
    \item Olympic khu vực Duyên Hải và đồng bằng Bắc Bộ
    \item Chọn HSGQG THPT Việt Nam $-$ VPhO 
    \item The United States Physics Olympiad $-$ USAPhO
    \item Gulf Physics Olympiad $-$ GPHO
    \item Pan Pearl River Delta Physics Olympiad (Olympic Vật lý khu vực Đồng bằng sông Châu Giang) $-$ PPRDPhO
    \item Fyziklani: http://online.fyziklani.cz/en/
    \item OPhO: https://opho.physoly.tech/ 
    \item International Zhautykov Olympiad $-$ IZho
    \item Asian Physics Olympiad $-$ APhO
    \item International Physics Olympiad $-$ IPhO
    \end{enumerate}
    
